
\documentclass[12pt]{article}
%\usepackage[final]{pdfpages}

\usepackage{graphicx}
\graphicspath{{/Users/kevinhayes/Documents/teaching/images/}}

\usepackage{tikz}
\usetikzlibrary{arrows}

\newcommand{\bbr}{\Bbb{R}}
\newcommand{\zn}{\Bbb{Z}^n}

%\usepackage{epsfig}
%\usepackage{subfigure}
\usepackage{amscd}
\usepackage{amssymb}
\usepackage{amsbsy}
\usepackage{amsthm}
\usepackage{natbib}
\usepackage{amsbsy}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{eurosym}
%\usepackage{beamerarticle}
\usepackage{txfonts}
\usepackage{fancyvrb}
\usepackage{fancyhdr}
\usepackage{natbib}
\bibliographystyle{chicago}

\usepackage{vmargin}
% left top textwidth textheight headheight
% headsep footheight footskip
\setmargins{2.0cm}{2.5cm}{16 cm}{22cm}{0.5cm}{0cm}{1cm}{1cm}
\renewcommand{\baselinestretch}{1.3}


\pagenumbering{arabic}
\begin{document}


\subsection{Types of Sets}
Sets can be classified into many types. Some of which are finite, infinite, subset, universal, proper, singleton set, etc.
%--------------------------------- %
\section*{The Universal Set and the Empty Set}
\begin{itemize}
	\item The first is the \textbf{\textit{universal set}}, typically denoted $U$. This set is all of the elements that we may choose from. This set may be different from one setting to the next. 
	
	\item For example one universal set may be the set of all real numbers, denoted $\mathbb{R}$, whereas for another problem the universal set may be the whole numbers $\{0, 1, 2,\ldots\}$.
	
	\item The other set that requires consideration is called the \textit{\textbf{empty set}}. The empty set is the unique set is the set with no elements. We write this as $\{ \}$ and denote this set by $\emptyset$.
\end{itemize}



%=================================================%
\subsection{Finite Set}
A set which contains a definite number of elements is called a finite set.

\subsubsection{Example} \[S=\{x|x \in N and 70 >x>50\}\]
\subsection{Infinite Set}
A set which contains infinite number of elements is called an infinite set.

\subsubsection{Example} \[S={x|x\in N  and x>10}\]
\subsection{Subset}
A set X is a subset of set Y (Written as $X \subseteq Y$) if every element of X is an element of set Y.

Example 1 − Let, $X={1,2,3,4,5,6}$ and Y={1,2}Y={1,2}. Here set Y is a subset of set X as all the elements of set Y is in set X. Hence, we can write Y⊆XY⊆X.

Example 2 − Let, $X={1,2,3}$ and Y={1,2,3}Y={1,2,3}. Here set Y is a subset (Not a proper subset) of set X as all the elements of set Y is in set X. Hence, we can write Y⊆XY⊆X.

\subsection{Proper Subset}
The term “proper subset” can be defined as “subset of but not equal to”. A Set X is a proper subset of set Y (Written as X⊂YX⊂Y) if every element of X is an element of set Y and |X|<|Y||X|<|Y|.

\subsubsection{Example} Let, $X={1,2,3,4,5,6}$ and Y={1,2}Y={1,2}. Here set Y⊂XY⊂X since all elements in YY are contained in XX too and XX has at least one element is more than set YY.

\subsection{Universal Set}
It is a collection of all elements in a particular context or application. All the sets in that context or application are essentially subsets of this universal set. Universal sets are represented as $U$.

\subsubsection{Example} We may define $U$ as the set of all animals on earth. In this case, set of all mammals is a subset of $U$, set of all fishes is a subset of $U$, set of all insects is a subset of $U$, and so on.

\subsection{Empty Set or Null Set}
An empty set contains no elements. It is denoted by ∅∅. As the number of elements in an empty set is finite, empty set is a finite set. The cardinality of empty set or null set is zero.

\subsubsection{Example} \[S={x|x\in N and 7<x<8}=∅\]



Another set which has a special letter to denote it is the set containing no elements. This is called
the empty or null set and denoted by the symbol (D. 
Example 2.6 The set of integers m such that m2 = 5 is the empty set. We could write
${mEZ:m2=5}:@.
\smallskip 
%----------------------------------------- %




\subsection{Singleton Set or Unit Set}
Singleton set or unit set contains only one element. A singleton set is denoted by {s}{s}.

\subsubsection{Example} $S={x|x\in N, 7<x<9} = {8}$

\subsection{Equal Set}
If two sets contain the same elements they are said to be equal.

\subsubsection{Example} If A={1,2,6}A={1,2,6} and B={6,1,2}B={6,1,2}, they are equal as every element of set A is an element of set B and every element of set B is an element of set A.

\section{Equivalent Set}
If the cardinalities of two sets are same, they are called equivalent sets.

\subsubsection{Example} If A={1,2,6}A={1,2,6} and B={16,17,22}B={16,17,22}, they are equivalent as cardinality of A is equal to the cardinality of B. i.e. |A|=|B|=3|A|=|B|=3
\subsection{Overlapping Set}
Two sets that have at least one common element are called overlapping sets.

In case of overlapping sets −

n(A∪B)=n(A)+n(B)−n(A∩B)n(A∪B)=n(A)+n(B)−n(A∩B)
n(A∪B)=n(A−B)+n(B−A)+n(A∩B)n(A∪B)=n(A−B)+n(B−A)+n(A∩B)
n(A)=n(A−B)+n(A∩B)n(A)=n(A−B)+n(A∩B)
n(B)=n(B−A)+n(A∩B)n(B)=n(B−A)+n(A∩B)
\subsubsection{Example} Let, A={1,2,6}A={1,2,6} and B={6,12,42}B={6,12,42}. There is a common element ‘6’, hence these sets are overlapping sets.

\section{Disjoint Set}
Two sets A and B are called disjoint sets if they do not have even one element in common. Therefore, disjoint sets have the following properties −

n(A∩B)=∅n(A∩B)=∅
n(A∪B)=n(A)+n(B)n(A∪B)=n(A)+n(B)
\subsubsection{Example} Let, A={1,2,6}A={1,2,6} and B={7,9,14}B={7,9,14}, there is not a single common element, hence these sets are overlapping sets.


%------------------------------------------------------%

\section*{Complement of a Set}
%(2.3.1) 
Consider the universal set $U$ such that
\[U=\{2,4,6,8,10,12,15\} \]
For each of the sets $A$,$B$,$C$ and $D$, specify the complement sets.
{
	\LARGE
	\begin{center}
		\begin{tabular}{|c|c|}
			\hline
			Set &\phantom{sp} Complement \phantom{sp}\\
			\hline \phantom{sp} $A=\{4,6,12,15\}$ \phantom{sp} &
			$A^{\prime}=\{2,8,10\}$ \\ \hline $B=\{4,8,10,15\}$ & \\ \hline
			$C=\{2,6,12,15\}$ & \\ \hline $D=\{8,10,15\}$ & \\ \hline
			
		\end{tabular}
	\end{center}
}




%--------------------------------- %
\subsection{Universal Set and the Empty Set}
The first is the \textbf{\textit{universal set}}, typically denoted $U$. This set is all of the elements that we may choose from. This set may be different from one setting to the next. 

For example one universal set may be the set of real numbers whereas for another problem the universal set may be the whole numbers $\{0, 1, 2,\ldots\}$.

The other set that requires consideration is called the \textit{\textbf{empty set}}. The empty set is the unique set is the set with no elements. We write this as $\{ \}$ and denote this set by $\emptyset$.





%---------------------------------------------------------------------------%
\subsection{Complement and universal set}

The universal set (if it exists), usually denoted U, is a set of which everything conceivable is a member. In pure set theory, normally sets are the only objects considered (unlike here, where we have also considered numbers, colours and books, for example); in this case U would be the set of all sets. (Non-set objects, where they are allowed, are called 'urelemente' and are discussed below.)

In the presence of a universal set we can define X′, the complement of X, to be $U−X$. X′ contains everything in the universe apart from the elements of X. We could alternatively have defined it as

\[X′ = \{x | \tilde (x\in X)\}\]
and U as the complement of the empty set.

{Equal and Equivalent Sets}

%%- \vspace{-1cm}
Difference between equal sets and equivalent sets

\begin{itemize}
	\item Consider the sets \textbf{A} and \textbf{B}
	\[ \boldsymbol{A} = \{ 1,2,3,4,5,6 \} \] 
	\[ \boldsymbol{B} = \{1,2,3,4,5,6 \} \]
	%%- \vspace{0.2cm}
	\item \textbf{A} and \textbf{B} are \textit{\textbf{equal}} sets because \textit{\textbf{all}} their
	elements are precisely the \textit{\textbf{same}}.
\end{itemize}



%---------------------------------------------------%


{Equal and Equivalent Sets}

%%- \vspace{-0.7cm}
Difference between equal sets and equivalent sets

\begin{itemize}
	\item Consider the sets \textbf{C} and \textbf{D}
	\[ \boldsymbol{C} = \{a,b,c,d,e,f\} \]  \[ \boldsymbol{D} = \{3,4,5,6,7,8\} \]
	%%- \vspace{0.2cm}
	\item \textbf{C} and \textbf{D} are \textit{\textbf{equivalent}} sets
	because the cardinality of both the sets is the same (i.e. 6.)
	\item However \textbf{C} and \textbf{D} are not equal, as they are comprised of different elements.
\end{itemize}






%---------------------------------------------------%


{Equal and Equivalent Sets}

%%- \vspace{-1cm}

\begin{itemize}
	\item Necessarily all equal sets are equivalent sets.
	\item But are equivalent sets equal sets?
	
	\item No, because equivalent sets are sets that have the \textit{\textbf{same}} cardinality but equal sets are sets that all
	their elements are precisely the \textit{\textbf{same}}. 
\end{itemize}

\textbf{Example}:
\begin{itemize} \item \textbf{X}=\{p,q,r\} and \textbf{Y}=\{1,2,3\} are equivalent sets 
	\item \textbf{E} =\{m,n,o,p\}
	and \textbf{F}=\{m,n,o,p\} are equal and equivalent sets
\end{itemize}
\end{document}
